Measuring Political Freedom Around the World

### 2020-11-04 slides.Rmd
added table to slide

---
title: "Measuring Political Freedom Around the World"
subtitle: " Joe Despres, Joe Sigler, Jacob Haywood"
institute: "MSU"
date: "updated: `r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

@@

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

>>>>

---
title: "Measuring Political Freedom Around the World"
subtitle: "Sabrina Ball, Joe Despres, Joe Sigler, Jacob Haywood"
date: "Last compiled `r format(Sys.time(), '%H:%M')`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

@@

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE, echo = FALSE)
library(gtsummary)
source(here::here("R", "visualization.R"))
options(digits = 3)
```

---
```{r echo=FALSE}
best_subsets %>% 
  mutate_if(is.numeric, round, 3) %>% 
  select(model, adj.r.squared) %>% 
DT::datatable(fillContainer = FALSE, options = list(pageLength = 6))
```
---
